\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-07-23 textos/dsrt/latex8.tex
latex8

\documentclass[conference]{IEEEtran}

@@

%\usepackage[brazil]{babel}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\malg: a novel interest management algorithm for distributed simulations of MMOGs}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{\IEEEauthorblockN{Carlos Eduardo Benevides Bezerra}
% \IEEEauthorblockA{Federal University of Rio Grande do Sul\\
% Bento Gonçalves, 9500, Porto Alegre, RS, Brazil\\
% E-mail: carlos.bezerra@inf.ufrgs.br}
% \and
% \IEEEauthorblockN{Fábio Reis Cecin}
% \IEEEauthorblockA{Federal University of Rio Grande do Sul\\
% Bento Gonçalves, 9500, Porto Alegre, RS, Brazil\\
% E-mail: frcecin@inf.ufrgs.br}
% \and
% \IEEEauthorblockN{Cláudio Fernando Resin Geyer}
% \IEEEauthorblockA{Federal University of Rio Grande do Sul\\
% Bento Gonçalves, 9500, Porto Alegre, RS, Brazil\\
% E-mail: geyer@inf.ufrgs.br}
% }

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%AQUI OS AUTORES
\author{\IEEEauthorblockN{Carlos Eduardo B. Bezerra,
	Fábio R. Cecin,
	Cláudio F. R. Geyer}
\IEEEauthorblockA{Federal University of Rio Grande do Sul\\
	Bento Gonçalves, 9500, Porto Alegre, RS, Brazil,\\
	Email: \{carlos.bezerra, fcecin, geyer\}@inf.ufrgs.br}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath

% :: OLD ABSTRACT ::
Traditionally, a central server is utilized to provide support to MMOGs (massively multiplayer online games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infrastructure, but critical questions remain. Examples of the problems relative to peer-to-peer MMOG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, we propose the utilization of geographically distributed lower-cost nodes, working as a distributed game server. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify the \malg\ algorithm, which is a novel refinement of the interest management technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2 and their results demonstrate that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.

% :: ABSTRACT++ BY FABIO ::
%Traditionally, a centralized server or cluster of server machines is employed to provide support for MMOGs (massively multiplayer online games), where the number of participants is in the order of tens of thousands. In order to minimize the maintenance cost of this infrastructure, much work has been done trying to create a fully decentralized or peer-to-peer model to support MMOGs, but some critical issues remain unsolved. Since there is no general availability of Internet-wide IP multicast routing, decentralization proposals usually require peers on home broadband links to upload real-time game traffic to several peers simultaneously, and widespread last-mile broadband technologies such as ADSL have low upstream capacities by design which are usually further capped by connectivity providers. This adds to the difficulty of maintaining the game simulation consistent among the peers, no matter how they are to be organized. In this work, we propose the use of geographically distributed lower-cost nodes, served by higher-end but still consumer-grade broadband links, which work together to act as a distributed MMOG serving entity. The distribution model and some related works are also presented. To address the communication cost imposed on those `super-peer' server nodes, we also propose a novel refinement to the area of interest technique which significantly reduces the bandwidth consumed by game update traffic. Simulations have been made with ns-2, comparing different area of interest algorithms. The results show that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
In the last years, electronic games have become very popular, specially MMOGs (massively multiplayer online games), where the number of simultaneous players is in the order tens of thousands \cite{cecin2004fsa}. World of Warcraft \cite{worldofwarcraft}, Lineage II \cite{lineage2} and Guild Wars \cite{guildwars} are successful examples of MMOGs.

@@

\section{Related Work}
\label{relatedwork}
%talvez deva reduzir esta seção.

@@

\section{Definitions}
\label{def}

@@

\section{Distribution Model}
\label{model}

@@

\section{Interest Management}
\label{aoi}

@@

\section{Graded Area of Interest}
%\subsection{Círculo com atenuação}
\label{gaoi}

@@

%           A                   A              A 
%\subsection{Ângulo de visão com área próxima e atenuação da freqüência de atualização}
\section{The \malg\ algorithm}
%View Angle with close area and update frequency attenuation
%V    A          C     A         U      F         A
\label{csmooth}

@@

\section{Simulation}
\label{sim}

@@

\section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to vary the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most up-to-date possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The development of this work was supported by the Funding for Studies and Projects (FINEP), a brazilian research agency, through the P2PSE project (P2PSE-5849-1).

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{dsrt}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \begin{thebibliography}{1}
% 
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
% 
% \end{thebibliography}

% that's all folks
\end{document}

>>>>

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

@@

%\usepackage[brazil]{babel}
%\usepackage[english]{babel}
\usepackage[latin1]{inputenc}

@@

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{\malg: a novel interest management algorithm for distributed simulations of MMOGs}

\author{Carlos Eduardo B. Bezerra, Fábio R. Cecin, Cláudio F. R. Geyer\\
	Informatics Institute\\
	Federal University of Rio Grande do Sul\\
	Bento Gonçalves, 9500, Porto Alegre, RS, Brazil\\
	\{carlos.bezerra,fcecin,geyer\}@inf.ufrgs.br\\
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
Traditionally, a central server is utilized to provide support to MMOGs (massively multiplayer online games), where the number of participants is in the order of tens of thousands. Much work has been done trying to create a fully peer-to-peer model to support this kind of application, in order to minimize the maintenance cost of its infrastructure, but critical questions remain. Examples of the problems relative to peer-to-peer MMOG support systems are: vulnerability to cheating, overload of the upload links of the peers and difficulty to maintain consistency of the simulation among the participants. In this work, we propose the utilization of geographically distributed lower-cost nodes, working as a distributed game server. The distribution model and some related works are also presented. To address the communication cost imposed to the servers, we specify the \malg\ algorithm, which is a novel refinement of the interest management technique, significantly reducing the necessary bandwidth. Simulations have been made with ns-2 and their results demonstrate that our approach achieves the least bandwidth utilization, with a 33.10\% maximum traffic reduction and 33.58\% average traffic reduction, when compared to other area of interest algorithms.
\end{abstract}

%------------------------------------------------------------------------- 
\Section{Introduction}

% no \IEEEPARstart
In the last years, electronic games have become very popular, specially MMOGs (massively multiplayer online games), where the number of simultaneous players is in the order tens of thousands \cite{cecin2004fsa}. World of Warcraft \cite{worldofwarcraft}, Lineage II \cite{lineage2} and Guild Wars \cite{guildwars} are successful examples of MMOGs.

@@

%------------------------------------------------------------------------- 
\section{Related Work}
\label{relatedwork}
%talvez deva reduzir esta seção.

@@

%------------------------------------------------------------------------- 
\section{Definitions}
\label{def}

@@

%------------------------------------------------------------------------- 
\section{Distribution Model}
\label{model}

@@

%------------------------------------------------------------------------- 
\section{Interest Management}
\label{aoi}

@@

%------------------------------------------------------------------------ 
\section{Graded Area of Interest}
%\subsection{Círculo com atenuação}
\label{gaoi}

@@

%------------------------------------------------------------------------- 
\section{The \malg\ algorithm}
%View Angle with close area and update frequency attenuation
%V    A          C     A         U      F         A
\label{csmooth}

@@

%------------------------------------------------------------------------- 
\section{Simulation}
\label{sim}

@@

%------------------------------------------------------------------------- 
\section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to vary the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most up-to-date possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.

%------------------------------------------------------------------------- 
\section*{Acknowledgment}

%The development of t
This work was supported by the Funding for Studies and Projects (FINEP), through the P2PSE project (P2PSE-5849-1), and by the National Research Council (CNPq).% FINEP and CNPq are brazilian research agencies.

%------------------------------------------------------------------------- 
%\nocite{ex1,ex2}
\bibliographystyle{latex8}
\bibliography{dsrt}

\end{document}
